NumPy---Array Programming in Python

### 2020-01-26 body.tex
Modified pycbc and eht-imaging text - more explicit.
I've modified the text related to a more detailed look at the
pycbc and eht-imaging libraries to be a bit more explicit.

I also added the neutron star merger example to the end of the
pycbc discussion as it is another incredible scientific
discovery supported by GWOs and pycbc.

For example, the \code{eht-imaging} library developed by the Event Horizon Telescope 
collaboration relies on many components of the scientific Python ecosystem.
NumPy arrays are used to store and manipulate numerical data at every step
in the processing chain: from raw data through calibration and image 
reconstruction.
Scipy is used to provide tools used in general image processing such as 
filtering and image alignment, while scikit-image provides higher-level
functionality such as edge filters and Hough transforms.
SciPy provides fundamental algorithms for scientific computing on arrays
including many mathematical, scientific, and engineering routines.
SciPy and NumPy are closely related and were developed together often
by the same people.
scikit-image is a popular technique-specific library,
which vastly extends the basic image processing tools provided by SciPy.
Other components of Scipy are used throughout the library, such as the
\code{scipy.optimize} package for handling general optimization tasks.
NetworkX \cite{SciPyProceedings_11} (the standard package for complex
network analysis) is used for image comparisons.
Astropy \cite{astropy:2013, astropy:2018} (a community-developed astronomy
libarary) is used in quite a few places,
primarily for I/O and time/coordinate transformations.
Matplotlib (the core library for generating publication-ready figures
and visualizations) is used for visualizing data throughout the analysis pipeline,
including the generation of the final image of the black hole.
% N.B. - most of this comes from introspecting the Image class defined in
% ehtim/image.py.

Tools for analyzing data from gravitational wave observatories such as LIGO
and Virgo are provided by the \code{pycbc} package, which was used in the first
detection of gravitationaly waves \cite{abbott2016observation} and in 
on-going analysis of data from LIGO and Virgo.
\code{pycbc} make extensive use of the scientific Python ecosystem.
The time-series data from the interferometers are stored in NumPy arrays,
while the \code{scipy.signal} is used to construct and apply filters to the
data.
Matplotlib is used to visualize data at all points along the analysis chain
including raw data from the instrumentation and the time-frequency 
visualization of the ``chirp'' from the binary black hole merger.

>>>>

For example, the \code{eht-imaging} library developed by the Event Horizon Telescope 
collaboration relies on many components of the scientific Python ecosystem.
NumPy arrays are used to store and manipulate numerical data at every step
in the processing chain: from raw data through calibration and image 
reconstruction.
Scipy is used to provide tools used in general image processing such as 
filtering and image alignment, while scikit-image provides higher-level
functionality such as edge filters and Hough transforms.
SciPy provides fundamental algorithms for scientific computing on arrays
including many mathematical, scientific, and engineering routines.
SciPy and NumPy are closely related and were developed together often
by the same people.
scikit-image is a popular technique-specific library,
which vastly extends the basic image processing tools provided by SciPy.
Other components of Scipy are used throughout the library, such as the
\code{scipy.optimize} package for handling general optimization tasks.
NetworkX \cite{SciPyProceedings_11} (the standard package for complex
network analysis) is used for analysis of consistency among image
comparisons.
Astropy \cite{astropy:2013, astropy:2018} (a community-developed astronomy
library) is used throughout the library,
primarily for I/O from standard astronomical file formats and time/coordinate
transformations.
Matplotlib (the core library for generating publication-ready figures
and visualizations) is used for visualizing data throughout the analysis pipeline,
including the generation of the final image of the black hole.
% N.B. - most of this comes from introspecting the Image class defined in
% ehtim/image.py and grepping the dependencies in requirements.txt

Tools for analyzing data from gravitational wave observatories such as LIGO
and Virgo are provided by the \code{pycbc} package, which was used in the first
detection of gravitational waves \cite{abbott2016observation} and in 
on-going analysis of data from LIGO and Virgo.
\code{pycbc} make extensive use of the scientific Python ecosystem.
The time-series data from the interferometers are stored in NumPy arrays,
while the \code{scipy.signal} is used to construct and apply filters to the
data.
Matplotlib is used to visualize data at all points along the analysis chain
including raw data from the instrumentation and the time-frequency 
visualization of the ``chirps'' that result from mergers of compact binaries
such as black holes\cite{abbott2016observation} and
neutron stars\cite{abbott2017multi}.
